Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-08 paper.tex
Shortened author list of reference paper
added preliminary text to results section
Switched to aasjournal citation style

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
% \usepackage{txfonts}

@@

\subsection{Navarro-Frenk-White (NFW) Profile}
The NFW profile has had some success in describing dark matter halos is both simulations and observations, though
\citep{Navarro1997}
\begin{equation}
\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
\end{equation}

@@

\section{Results}

@@

\bibliographystyle{plainnat}
\bibliography{references}

>>>>

\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[square]{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
% \usepackage{txfonts}

@@

\subsection{Navarro-Frenk-White (NFW) Profile}
The NFW profile has had some success in describing dark matter halos in both simulations and observations, though
\citep{Navarro1997}
It is characterized by a scale radius $r_s$ and a dimensionless parameter $\delta_c$, sometimes called the characteristic overdensity \citep{Wright2000}.
\begin{equation}
\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
\end{equation}

@@

\section{Results}
%\begin{figure}
%    \centering
%    \includegraphics{nfwfitparams.pdf}
%    \label{}
%\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics{isothermalfitparams.pdf}
%    \label{}
%\end{figure}

@@

\bibliographystyle{aasjournal}
\bibliography{references}
